---
title: "Analysis"
output:
  html_document:
    df_print: paged
date: "2024-05-14"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, results='asis')
```


```{r}
library(tidyr)
library(stringr)
library(dplyr)
library(ggplot2)
library(readxl)
library(kableExtra)
library(knitr)
```


```{r}
DataExtractionTable <- read_excel("DataExtractionTable_JL.xlsx")


data<-DataExtractionTable%>%
 mutate(across(c(everything(), -c(StudyId,G_Country,G_Year_Pub,TS_SR_n,TS_other,SR_n_databases,comments)), ~ifelse(.=="yes",TRUE,FALSE)))%>%
 mutate(across(c(everything(), -c(StudyId,G_Country,G_Year_Pub,TS_SR_n,TS_other,SR_n_databases,comments)), ~ifelse(is.na(.),FALSE,.)))
```

## Type of study

Important throughout: within one report more than one study can be found.


```{r}
data_summary_studytype<-data %>%
  select(StudyId,G_Year_Pub,starts_with("TS_"),-c(TS_SR_n,TS_other)) %>% 
  pivot_longer(cols = starts_with("TS_")) %>% 
  filter(value==T) %>% 
  group_by(G_Year_Pub,name) %>% 
  count() %>% 
  ungroup() %>% 
  group_by(name) %>% mutate(n_per_studytype=sum(n)) %>% ungroup() %>% 
  group_by(G_Year_Pub) %>% mutate(n_per_year=sum(n)) %>% ungroup() %>% 
  mutate(name=gsub("TS_","",name),
         name=gsub("SR_yn","SR",name),
         name=gsub("Literature_review","Literature review",name),
         name_label=paste0(name,", n = ",n_per_studytype)) 

data_summary_studytype %>% 
  select(name,n_per_studytype) %>% 
  unique() %>% 
  arrange(-n_per_studytype) %>% 
  rbind(.,cbind(name="Total reports",n_per_studytype=nrow(DataExtractionTable))) %>% 
  rename(`Study type`=name,
         n=n_per_studytype) %>% 
  kable(caption = "Overview of the types of studies extracted",booktabs = TRUE) %>% 
  kable_styling(full_width = F,position ="left")
```
<br>
<br>

#### Graphical overview of the studies extracted over the years

```{r}
data_summary_studytype %>% 
  ggplot(aes(x=G_Year_Pub,y=n))+
  geom_bar(stat="identity",aes(fill=reorder(name_label,n_per_studytype)))+
  theme_minimal()+
  theme(
    legend.title = element_blank(),
    panel.grid.minor = element_blank()
  )+
  scale_fill_manual(values=c("#fd7f6f", "#7eb0d5", "#b2e061",  "#ffee65", "#beb9db"))+
  labs(x="Year",y="n types of study")
```
<br>
<br>

#### Proportion of each study type over all the studies screened

```{r, fig.height=3,fig.width=7}
data_summary_studytype %>% 
  mutate(n_withoutstudy=nrow(DataExtractionTable)-n_per_studytype,
    proportion_studypresent=n_per_studytype/nrow(DataExtractionTable),
         proportion_study_notpresent=1-proportion_studypresent) %>% 
  select(name,n_per_studytype,name_label,proportion_studypresent,proportion_study_notpresent,n_withoutstudy) %>% 
  unique()  %>% 
  pivot_longer(cols=c(n_per_studytype,n_withoutstudy),names_to="studypresent",values_to="proportion") %>%  
  mutate(studypresent=ifelse(studypresent=="n_per_studytype","Yes","No")) %>% 
  ggplot(aes(y=name,x=proportion))+
  geom_col(position="stack",aes(fill=studypresent))+
  theme_minimal()+
  theme(axis.title.y = element_blank(),
        legend.title = element_blank())+
  scale_fill_manual(values=c("#7eb0d5", "#ffee65"))+
  labs(x="n studies")
```
<br>
<br>

## Systematic Reviews items
Important: even if a systematic review wasn't recorded because it didn't fit our inclusion criteria, we recorded each item independently (for instance: in a report a systematic review was conducted, a flowchart reported, involving two reviewers, but only 1 database was searched. This wouldn't categorize as SR, but the item flowchart and reviewers were recorded)
<br>

```{r}
data_summary_SRs<-data %>% 
  select(G_Year_Pub,starts_with("SR_"),-SR_n_databases) %>% 
  pivot_longer(!G_Year_Pub) %>% 
  mutate(value=ifelse(value==T,1,0)) %>% 
  group_by(G_Year_Pub,name,value) %>% 
  summarise(n=sum(value)) %>% 
  ungroup() %>% 
  filter(value==1) %>% 
  group_by(name) %>% mutate(n_per_studytype=sum(n)) %>% ungroup() %>% 
  group_by(G_Year_Pub) %>% mutate(n_per_year=sum(n)) %>% ungroup()
  
data_summary_SRs %>% 
select(name,n_per_studytype) %>% 
  unique() %>% 
  arrange(-n_per_studytype) %>% 
  mutate(name=gsub("SR_","",name),
         name=str_to_sentence(name),
         name=gsub("Searchstring","Search string",name),
         name=gsub("Metanaalysis","Meta-analysis",name)
         ) %>% 
  rbind(.,cbind(name="Total reports",n_per_studytype=nrow(DataExtractionTable))) %>% 
  rename(`Study type`=name,
         n=n_per_studytype) %>% 
  kbl(caption = "Overview of the types of SR items extracted") %>% 
  kable_styling(full_width = F,position ="left")
```
Search string: search string was present. Databases: 2 or more databases were searched. Flowchart: a flowchart was present. Reviewers: two or more reviewers screened the literature. Protocol: a a-priori protocol was written and published. Rob: a risk of bias analysis was performed. Meta-analysis: a meta-analysis was performed.

<br>
<br>

#### SR items extracted over the years
```{r}
data_summary_SRs %>% 
  select(G_Year_Pub,name,n) %>% 
  merge(.,data %>% group_by(G_Year_Pub) %>% count() %>% rename(n_studies_per_year=n),by="G_Year_Pub",all.y=T) %>% 
  group_by(G_Year_Pub) %>% mutate(count_col_label=1:n()) %>% ungroup() %>% 
  mutate(count_col_label=ifelse(count_col_label==1,n_studies_per_year,NA),
         name=gsub("SR_","",name), 
         name=str_to_sentence(name)) %>% 
  ggplot(aes(x=G_Year_Pub))+
  # geom_col(aes(y=count_col_label))+
  geom_col(aes(y=n,fill=name))+
  theme_minimal()+
  theme(
    panel.grid.minor = element_blank(),
    legend.title = element_blank()
  )+
  scale_fill_manual(values=c("#fd7f6f", "#7eb0d5", "#b2e061", "#bd7ebe", "#ffb55a", "#ffee65", "#beb9db"))+
  labs(x="Year")
```

#### SR items extracted over the years
Top part of the figure: studies extracted and proportion of SRs (dark gray) of the total studies extracted per year (light gray). Lower part of the figure: proportion of the various items of SRs extracted. The idea was to display everything in one figure **but** it has the problem of the y-scale. The number of studies has a straightforward scale, but if the raw numbers are diplayed in the lower part of the graph, it would not match the upper part. So this is still a work-in-progress
<br>

```{r}
upper_plot_data<-data_summary_SRs %>% 
  rename(nSR_per_year=n_per_year,
         nSR_oer_item=n_per_studytype) %>% 
  mutate(name=gsub("SR_","",name), 
         name=str_to_sentence(name))


lower_plot_data<-data %>% 
  group_by(G_Year_Pub,TS_SR_yn) %>% 
  count() %>% 
  mutate(TS_SR_yn=ifelse(TS_SR_yn==T,"Systematic Reviews","Other studies"))


ggplot()+
  geom_bar(data=upper_plot_data,aes(x=G_Year_Pub,y=-n/2,fill=name),stat="identity")+
  geom_bar(data=lower_plot_data,aes(x=G_Year_Pub,y=n,fill=TS_SR_yn),stat="identity")+   scale_fill_manual(values=c("Databases"="#fd7f6f",
                             "Flowchart"= "#7eb0d5",
                             "Metanaalysis"= "#b2e061",
                             "Protocol"= "#bd7ebe",
                             "Reviewers"= "#ffb55a",
                             "Rob"= "#ffee65",
                             "Searchstring"= "#beb9db",
                             "Systematic Reviews"="gray50",
                             "Other studies"="gray80"),
                             breaks=c("Other studies",
"Systematic Reviews",
"Searchstring",
"Rob",
"Reviewers",
"Protocol",
"Metanaalysis",
"Flowchart",
"Databases"

))+  theme_minimal()+
  theme(
    panel.grid.minor = element_blank(),
    legend.title = element_blank()
  )+
  scale_y_continuous(breaks=c(0,10,20))+
  labs(y="proportion of SR items, n reports",x="Year of publication")

```

<br>
<br>

### Databases used
```{r}
databases_SR_n<-pull(data %>% 
  select(SR_n_databases) %>% 
  drop_na())
```

The number database used ranged from `r min(databases_SR_n)` to `r max(databases_SR_n)`, with a median of `r median(databases_SR_n)`


<br><br>



