---
title: "Analysis"
output:
  html_document:
    df_print: paged
date: "2024-05-14"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, results='asis')
```

```{r}
library(tidyr)
library(stringr)
library(dplyr)
library(ggplot2)
library(readxl)
library(kableExtra)
library(knitr)
library(readr)
library(rcrossref)
library(writexl)

StudyList_EFSA <- read_excel("StudyList_EFSA_furtherextraction.xlsx", 
    sheet = "All_furtherextraction")
```

```{r message=FALSE, warning=FALSE}
# EFSA_dois<-data.frame()
# 
# for(i in StudyList_EFSA$Title){
# 
# result <- cr_works(query = i, limit = 1)$data$doi
# 
# if (is.na(result)){
#   result<-NA
# } else {
#   result<-result
# }
# 
# df<-data.frame(cbind(Title=i,doi=result))
# EFSA_dois<-rbind(EFSA_dois,df)
# 
# }

# write_xlsx(EFSA_dois,"EFSA_dois.xlsx")

EFSA_dois <- read_excel("EFSA_dois.xlsx")
```

```{r}
Data_studyscopes<-StudyList_EFSA %>% 
  rename(Subscope=5) %>% 
  merge(.,EFSA_dois,by="Title")
```

# Species

(I actually don't think we need a figure of this but I was trying something out)

```{r}
Species_used_summary<-Data_studyscopes%>%
  separate_rows(species, sep = ",\\s*") %>% 
  select(species) %>% 
  filter(!is.na(species)) %>% 
  mutate(species=case_when(
    species=="horse"~"horses",
    species=="boar"~"boars",
    species=="quail"~"quails",
    species=="sheeps"~"sheep",
    species=="NA"~NA,
    TRUE~species
  )) %>% 
  group_by(species) %>% 
  count() %>% 
  arrange(-n)

Species_used_summary%>% 
  kbl(caption = "Overview of the species in focus") %>% 
  kable_styling(full_width = F,position ="left")%>%
  scroll_box(height = "400px")

Species_used_summary %>%
  mutate(species=ifelse(n<10,"Others",species)) %>% 
  group_by(species) %>% 
  summarise(n=sum(n)) %>% 
  mutate(order=ifelse(species=="Others",1,2)) %>% 
  arrange(-order,-n) %>% 
  mutate(order_y=1:n(),
         label=paste0(str_to_title(species),", n = ",n),
         cumsum=cumsum(n)) %>% 
ggplot(aes(x = 1, y = n, fill = reorder(label,-order_y))) +
  geom_col(width = 0.3)+
  geom_text(aes(label=label,y=cumsum-n/2),angle=270,hjust=0.5)+
    scale_fill_manual(values=c("#dedede","#fd7f6f", "#7eb0d5", "#b2e061", "#bd7ebe", "#ffb55a", "#ffee65", "#beb9db"),name="Species")+
  scale_x_reverse()+
  theme_minimal()+
  theme(
    legend.title = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "bottom",
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    panel.grid.major.y = element_blank()
  )+
  coord_flip()
```

# Scope of the study

```{r}
Studyscopes_summary<-Data_studyscopes %>% 
  mutate(Scope=case_when(
    Scope=="disesase"~"disease",
    TRUE~Scope
  )) %>% 
  group_by(Scope,Subscope) %>% 
  summarise(n_per_subscope=n()) %>% 
  ungroup() 

Studyscopes_summary%>% 
  kbl(caption = "Overview of the types of SR items extracted") %>% 
  kable_styling(full_width = F,position ="left")

Studyscopes_summary %>% 
  group_by(Scope) %>% 
  mutate(n_per_scope=sum(n_per_subscope))%>% 
  select(Scope,n_per_scope) %>% unique() %>% 
  kbl(caption = "Overview of the scope of each report") %>% 
  kable_styling(full_width = F,position ="left")
```

```{r}
DataExtractionTable <- read_excel("DataExtractionTable_JL.xlsx")

data<-
  DataExtractionTable %>% 
  mutate(TS_other=ifelse(grepl("ad hoc",TS_other),"AHL ad-hoc",TS_other)) %>% 
  mutate(TS_other=case_when(
    TS_other=="Evaluation of four provided studies"~"Evaluation of previous studies",
    TS_other=="Evaluation of three provided studies"~"Evaluation of previous studies",
    TS_other=="expert knowledge elicitation,"~"expert knowledge elicitation",
    TS_other=="qualtive"~"qualitative",
    TS_other=="risk assesment"~"risk assessment",
    TS_other=="risk assessment and questionaires for EU countries"~"risk assessment, questionaire",
    TS_other=="study designs"~"study design",
    TS_other=="two stakeholder meetings"~"stakeholder meeting",
    TRUE~TS_other
  )) %>% 
    mutate(TS_AHL=ifelse(TS_other=="AHL ad-hoc","yes",NA))%>%
 mutate(across(c(everything(), -c(StudyId,G_Country,G_Year_Pub,TS_SR_n,TS_other,SR_n_databases,comments)), ~ifelse(.=="yes",TRUE,FALSE)))%>%
 mutate(across(c(everything(), -c(StudyId,G_Country,G_Year_Pub,TS_SR_n,TS_other,SR_n_databases,comments)), ~ifelse(is.na(.),FALSE,.)))
```

# Type of study

Important throughout: within one report more than one study can be found.

```{r, fig.height=3,fig.width=7}
data_summary_studytype<-
  data %>%
  select(StudyId,G_Year_Pub,starts_with("TS_"),-c(TS_SR_n,TS_other)) %>% 
  pivot_longer(cols = starts_with("TS_")) %>% 
  filter(value==T) %>% 
  group_by(name) %>% 
  summarise(n_per_studytype=n()) %>% 
  ungroup() %>% 
  mutate(name=gsub("TS_","",name),
         name=case_when(name=="Literature_review"~"Literature review",
                   name=="SR_yn"~"Systematic review",
                   name=="Primary_study"~"Primary study",
                   TRUE~name
                   ))

data_summary_studytype %>%
  kbl(caption = "Overview of the study types") %>% 
  kable_styling(full_width = F,position ="left")

data_summary_studytype %>% 
  mutate(n_withoutstudy=nrow(DataExtractionTable)-n_per_studytype,
    proportion_studypresent=n_per_studytype/nrow(DataExtractionTable),
         proportion_study_notpresent=1-proportion_studypresent) %>% 
  unique()  %>% 
  pivot_longer(cols=c(n_per_studytype,n_withoutstudy),names_to="studypresent",values_to="proportion") %>%  
  mutate(studypresent=ifelse(studypresent=="n_per_studytype","Present","Not present")) %>%
  merge(.,data_summary_studytype,by="name") %>% 
  ggplot(aes(y=reorder(name,n_per_studytype),x=proportion))+
  geom_col(position="stack",aes(fill=studypresent))+
  geom_text(data=. %>% filter(studypresent=="Present"),aes(label=paste0(name,", n = ",proportion),x=-2),size=2.8,hjust=1, color="#585858")+
  theme_minimal()+
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        legend.title = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major.y =element_blank())+
  scale_fill_manual(values=c("#7eb0d5", "#ffee65"))+
  scale_x_continuous(breaks=seq(0,150,50))+
  labs(x="n studies")+
  coord_cartesian(xlim=c(-40,NA))
```

<br> <br>

### Graphical overview of the studies extracted over the years

```{r}
data %>%
  select(StudyId,G_Year_Pub,starts_with("TS_"),-c(TS_SR_n,TS_other)) %>% 
  pivot_longer(cols = starts_with("TS_")) %>% 
  filter(value==T) %>% 
  group_by(G_Year_Pub,name) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(name=gsub("TS_","",name),
         name=case_when(name=="Literature_review"~"Literature review",
                   name=="SR_yn"~"Systematic review",
                   name=="Primary_study"~"Primary study",
                   TRUE~name
                   )) %>% 
  mutate(name=factor(name,levels=c("Primary study","Observational","Database","Survey","Systematic review","AHL","Literature review"))) %>% 
  # mutate(name=factor(name,levels=c("Literature review","AHL","Systematic review","Survey","Database","Observational","Primary study"))) %>% 
  ggplot(aes(x=G_Year_Pub,y=n))+
  geom_bar(stat="identity",aes(fill=name))+
  theme_minimal()+
  theme(
    legend.title = element_blank(),
    panel.grid.minor = element_blank()
  )+
    scale_fill_manual(values=c("#b2e061", "#fd7f6f", "#ffee65", "#beb9db", "#ffb55a", "#7eb0d5","#dedede"))+

  labs(x="Year",y="n types of study")

```

<br> <br>

# Systematic Reviews items

Important: even if a systematic review wasn't recorded because it didn't fit our inclusion criteria, we recorded each item independently (for instance: in a report a systematic review was conducted, a flowchart reported, involving two reviewers, but only 1 database was searched. This wouldn't categorize as SR, but the item flowchart and reviewers were recorded) <br>

```{r}
data_summary_SRs<-data %>% 
  select(G_Year_Pub,starts_with("SR_"),-SR_n_databases) %>% 
  pivot_longer(!G_Year_Pub) %>% 
  mutate(value=ifelse(value==T,1,0)) %>% 
  group_by(G_Year_Pub,name,value) %>% 
  summarise(n=sum(value)) %>% 
  ungroup() %>% 
  filter(value==1) %>% 
  group_by(name) %>% mutate(n_per_studytype=sum(n)) %>% ungroup() %>% 
  group_by(G_Year_Pub) %>% mutate(n_per_year=sum(n)) %>% ungroup()
  
data_summary_SRs %>% 
select(name,n_per_studytype) %>% 
  unique() %>% 
  arrange(-n_per_studytype) %>% 
  mutate(name=gsub("SR_","",name),
         name=str_to_sentence(name),
         name=gsub("Searchstring","Search string",name),
         name=gsub("Metanaalysis","Meta-analysis",name)
         ) %>% 
  rbind(.,cbind(name="Total reports",n_per_studytype=nrow(DataExtractionTable))) %>% 
  rename(`Study type`=name,
         n=n_per_studytype) %>% 
  kbl(caption = "Overview of the types of SR items extracted") %>% 
  kable_styling(full_width = F,position ="left")
```

Search string: search string was present. Databases: 2 or more databases were searched. Flowchart: a flowchart was present. Reviewers: two or more reviewers screened the literature. Protocol: a a-priori protocol was written and published. Rob: a risk of bias analysis was performed. Meta-analysis: a meta-analysis was performed.

<br> <br>

### SR items extracted over the years

```{r}
data_summary_SRs %>% 
  filter(name!="SR_label_SR") %>% 
  filter(name!="SR_label_ELS") %>% 
  filter(name!="SR_label_LR") %>% 
  select(G_Year_Pub,name,n) %>% 
  merge(.,data %>% group_by(G_Year_Pub) %>% count() %>% rename(n_studies_per_year=n),by="G_Year_Pub",all.y=T) %>% 
  group_by(G_Year_Pub) %>% mutate(count_col_label=1:n()) %>% ungroup() %>% 
  mutate(count_col_label=ifelse(count_col_label==1,n_studies_per_year,NA),
         name=gsub("SR_","",name), 
         name=str_to_sentence(name)) %>% 
  ggplot(aes(x=G_Year_Pub))+
  # geom_col(aes(y=count_col_label))+
  geom_col(aes(y=n,fill=name))+
  theme_minimal()+
  theme(
    panel.grid.minor = element_blank(),
    legend.title = element_blank()
  )+
  scale_fill_manual(values=c("#fd7f6f", "#7eb0d5", "#b2e061", "#bd7ebe", "#ffb55a", "#ffee65", "#beb9db"))+
  labs(x="Year")
```

### SR items extracted over the years

Top part of the figure: studies extracted and proportion of SRs (dark gray) of the total studies extracted per year (light gray). Lower part of the figure: proportion of the various items of SRs extracted. The idea was to display everything in one figure **but** it has the problem of the y-scale. The number of studies has a straightforward scale, but if the raw numbers are diplayed in the lower part of the graph, it would not match the upper part. So this is still a work-in-progress <br>

```{r}
upper_plot_data<-data_summary_SRs %>% 
  rename(nSR_per_year=n_per_year,
         nSR_oer_item=n_per_studytype) %>% 
  mutate(name=gsub("SR_","",name), 
         name=str_to_sentence(name))


lower_plot_data<-data %>% 
  group_by(G_Year_Pub,TS_SR_yn) %>% 
  count() %>% 
  mutate(TS_SR_yn=ifelse(TS_SR_yn==T,"Systematic Reviews","Other studies"))


ggplot()+
  geom_bar(data=upper_plot_data,aes(x=G_Year_Pub,y=-n/2,fill=name),stat="identity")+
  geom_bar(data=lower_plot_data,aes(x=G_Year_Pub,y=n,fill=TS_SR_yn),stat="identity")+   scale_fill_manual(values=c("Databases"="#fd7f6f",
                             "Flowchart"= "#7eb0d5",
                             "Metanaalysis"= "#b2e061",
                             "Protocol"= "#bd7ebe",
                             "Reviewers"= "#ffb55a",
                             "Rob"= "#ffee65",
                             "Searchstring"= "#beb9db",
                             "Systematic Reviews"="gray50",
                             "Other studies"="gray80"),
                             breaks=c("Other studies",
"Systematic Reviews",
"Searchstring",
"Rob",
"Reviewers",
"Protocol",
"Metanaalysis",
"Flowchart",
"Databases"

))+  theme_minimal()+
  theme(
    panel.grid.minor = element_blank(),
    legend.title = element_blank()
  )+
  scale_y_continuous(breaks=c(0,10,20))+
  labs(y="proportion of SR items, n reports",x="Year of publication")

```

<br> <br>

### Databases used

```{r}
databases_SR_n<-pull(data %>% 
  select(SR_n_databases) %>% 
  drop_na())
```

The number database used ranged from `r min(databases_SR_n)` to `r max(databases_SR_n)`, with a median of `r median(databases_SR_n)`

### Classification of reviews

```{r}
items_extracted_SR_count<-data %>% 
  select(TS_SR_yn,c(starts_with("SR_"),-SR_n_databases,-starts_with("SR_label_"))) %>%
  mutate(Any_SR_True = rowSums(select(., starts_with("SR_")) == TRUE) > 0) %>% 
  select(TS_SR_yn,Any_SR_True) %>% 
  summarise(SR_extracted=sum(TS_SR_yn),
            SR_items=sum(Any_SR_True))
```

`r sum(data$SR_label_ELS)` reviews were classified as ELS (extensive literature reviews). `r sum(data$SR_label_SR)` reviews were classified as systematic reviews.`r sum(data$TS_SR_yn)-(sum(data$SR_label_ELS)+sum(data$SR_label_SR))` were classified as neither, but were annotated by us as SR.

Even though only `r items_extracted_SR_count$SR_extracted` SRs were extracted according to our a-priori criteria, various items of a systematic review were extracted from `r items_extracted_SR_count$SR_items` studies.

<br><br>

```{r}
# save.image("image.RData")
```
