---
title: "Analysis"
output:
  html_document:
    df_print: paged
date: "2024-05-14"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, results='asis')
```

```{r}
library(tidyr)
library(stringr)
library(dplyr)
library(ggplot2)
library(readxl)
library(kableExtra)
library(knitr)
library(readr)
library(rcrossref)
library(writexl)
```


```{r}
StudyList_EFSA <- read_excel("StudyList_EFSA_furtherextraction.xlsx", 
    sheet = "All_furtherextraction")
```

```{r message=FALSE, warning=FALSE}
# EFSA_dois<-data.frame()
# 
# for(i in StudyList_EFSA$Title){
# 
# result <- cr_works(query = i, limit = 1)$data$doi
# 
# if (is.na(result)){
#   result<-NA
# } else {
#   result<-result
# }
# 
# df<-data.frame(cbind(Title=i,doi=result))
# EFSA_dois<-rbind(EFSA_dois,df)
# 
# }

# write_xlsx(EFSA_dois,"EFSA_dois.xlsx")

EFSA_dois <- read_excel("EFSA_dois.xlsx")
```

```{r}
Data_studyscopes<-StudyList_EFSA %>% 
  rename(Subscope=5) %>% 
  merge(.,EFSA_dois,by="Title")
```

# Species

(I actually don't think we need a figure of this but I was trying something out)

```{r fig.width=3,fig.height=6}
Species_used_summary<-Data_studyscopes%>%
  separate_rows(species, sep = ",\\s*") %>% 
  select(species) %>% 
  filter(!is.na(species)) %>% 
  mutate(species=case_when(
    species=="horse"~"horses",
    species=="boar"~"boars",
    species=="quail"~"quails",
    species=="sheeps"~"sheep",
    species=="NA"~NA,
    TRUE~species
  )) %>% 
  group_by(species) %>% 
  count() %>% 
  arrange(-n)

Species_used_summary%>% 
  kbl(caption = "Overview of the species in focus") %>% 
  kable_styling(full_width = F,position ="left")%>%
  scroll_box(height = "400px")

Species_used_summary %>%
  mutate(species=ifelse(n<10,"Others",species)) %>% 
  group_by(species) %>% 
  summarise(n=sum(n)) %>% 
  mutate(order=ifelse(species=="Others",1,2)) %>% 
  arrange(-order,-n) %>% 
  mutate(order_y=1:n(),
         label=paste0(str_to_title(species),", n = ",n),
         cumsum=cumsum(n)) %>% 
ggplot(aes(x = 1, y = n, fill = reorder(label,-order_y))) +
  geom_col(width = 0.3)+
  geom_text(aes(label=label,y=cumsum-n/2),hjust=0.5)+
    scale_fill_manual(values=c("#dedede","#fd7f6f", "#7eb0d5", "#b2e061", "#bd7ebe", "#ffb55a", "#ffee65", "#beb9db"),name="Species")+
  scale_y_reverse()+
  theme_minimal()+
  theme(
    legend.title = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "none",
    axis.title = element_blank(),
    axis.text = element_blank(),
    panel.grid.major = element_blank()
  )
```

# Scope of the study

```{r}
Studyscopes_summary<-Data_studyscopes %>% 
  mutate(Scope=case_when(
    Scope=="disesase"~"disease",
    TRUE~Scope
  )) %>% 
  group_by(Scope,Subscope) %>% 
  summarise(n_per_subscope=n()) %>% 
  ungroup() 

Studyscopes_summary%>% 
  kbl(caption = "Overview of the types of SR items extracted") %>% 
  kable_styling(full_width = F,position ="left")

Studyscopes_summary %>% 
  group_by(Scope) %>% 
  mutate(n_per_scope=sum(n_per_subscope))%>% 
  select(Scope,n_per_scope) %>% unique() %>% 
  kbl(caption = "Overview of the scope of each report") %>% 
  kable_styling(full_width = F,position ="left")
```

```{r}
DataExtractionTable <- read_excel("DataExtractionTable_JL.xlsx")

data<-
  DataExtractionTable %>% 
  mutate(TS_other=ifelse(grepl("ad hoc",TS_other),"AHL ad-hoc",TS_other)) %>% 
  mutate(TS_other=case_when(
    TS_other=="Evaluation of four provided studies"~"Evaluation of previous studies",
    TS_other=="Evaluation of three provided studies"~"Evaluation of previous studies",
    TS_other=="expert knowledge elicitation,"~"expert knowledge elicitation",
    TS_other=="qualtive"~"qualitative",
    TS_other=="risk assesment"~"risk assessment",
    TS_other=="risk assessment and questionaires for EU countries"~"risk assessment, questionaire",
    TS_other=="study designs"~"study design",
    TS_other=="two stakeholder meetings"~"stakeholder meeting",
    TRUE~TS_other
  )) %>% 
    mutate(TS_AHL=ifelse(TS_other=="AHL ad-hoc","yes",NA))%>%
 mutate(across(c(everything(), -c(StudyId,G_Country,G_Year_Pub,TS_SR_n,TS_other,SR_n_databases,comments)), ~ifelse(.=="yes",TRUE,FALSE)))%>%
 mutate(across(c(everything(), -c(StudyId,G_Country,G_Year_Pub,TS_SR_n,TS_other,SR_n_databases,comments)), ~ifelse(is.na(.),FALSE,.)))
```

# Figure 1

Important throughout: within one report more than one study can be found.

```{r, fig.height=3,fig.width=7}
data_summary_studytype<-
  data %>%
  select(StudyId,G_Year_Pub,starts_with("TS_"),-c(TS_SR_n,TS_other)) %>% 
  pivot_longer(cols = starts_with("TS_")) %>% 
  filter(value==T) %>% 
  group_by(name) %>% 
  summarise(n_per_studytype=n()) %>% 
  ungroup() %>% 
  mutate(name=gsub("TS_","",name),
         name=case_when(name=="Literature_review"~"Literature review",
                   name=="SR_yn"~"Systematic review",
                   name=="Primary_study"~"Primary study",
                   TRUE~name
                   ))

data_summary_studytype %>%
  kbl(caption = "Overview of the study types") %>% 
  kable_styling(full_width = F,position ="left")

data_summary_studytype %>% 
  mutate(n_withoutstudy=nrow(DataExtractionTable)-n_per_studytype,
    proportion_studypresent=n_per_studytype/nrow(DataExtractionTable),
         proportion_study_notpresent=1-proportion_studypresent) %>% 
  unique()  %>% 
  pivot_longer(cols=c(n_per_studytype,n_withoutstudy),names_to="studypresent",values_to="proportion") %>%  
  mutate(studypresent=ifelse(studypresent=="n_per_studytype","Present","Not present")) %>%
  merge(.,data_summary_studytype,by="name") %>% 
  ggplot(aes(y=reorder(name,n_per_studytype),x=proportion))+
  geom_col(position="stack",aes(fill=studypresent))+
  geom_text(data=. %>% filter(studypresent=="Present"),aes(label=paste0(name,", n = ",proportion),x=-2),size=2.8,hjust=1, color="#585858")+
  theme_minimal()+
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        legend.title = element_blank(),
    plot.margin = margin(0, 0, 0, 10),
        panel.grid.minor = element_blank(),
        legend.position = "none",
        panel.grid.major.y =element_blank())+
  scale_fill_manual(values=c("#7eb0d5", "#ffee65"))+
  scale_x_continuous(breaks=seq(0,150,50))+
  labs(x="n studies")+
  coord_cartesian(xlim=c(-40,NA))

ggsave("Figure1.png",dpi=300,height=3,width=7,bg="white")
```

<br> <br>

# Figure 2
Overview of the types of studies over the years (percentage of all the studies for that year)

```{r}
data %>% 
  select(StudyId,G_Year_Pub,starts_with("TS_"),-c(TS_SR_n,TS_other)) %>% 
  pivot_longer(cols = starts_with("TS_")) %>% 
  filter(value==T) %>% 
  group_by(G_Year_Pub,name) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(name=gsub("TS_","",name),
         name=case_when(name=="Literature_review"~"Literature review",
                   name=="SR_yn"~"Systematic review",
                   name=="Primary_study"~"Primary study",
                   TRUE~name
                   ))  %>% 
  # mutate(name=factor(name,levels=c("Primary study","Observational","Database","Survey","Systematic review","AHL","Literature review"))) %>% 
  group_by(name) %>% mutate(order_facet=sum(n)) %>% ungroup() %>% 
  mutate(facet_var_ordered = factor(name, levels = unique(name[order(-order_facet)]))) %>% 
  merge(.,data %>% group_by(G_Year_Pub) %>% count() %>% rename(n_per_year=n),by="G_Year_Pub") %>% 
   mutate(perc_TS=n/n_per_year) %>% 
  filter(name!="Primary study") %>%
  ggplot(aes(x=G_Year_Pub,y=perc_TS))+
  geom_bar(stat="identity",aes(fill=name)) +
  facet_wrap(.~facet_var_ordered)+
  scale_fill_manual(values=c("AHL"="#fd7f6f","Observational"= "#7eb0d5","Database"= "#b2e061","Systematic review"= "#bd7ebe","Survey"= "#ffb55a","Literature review"= "#ffee65"))+
  theme_minimal()+
  theme(
    panel.grid.minor = element_blank(),
    legend.title = element_blank(),
    legend.position = "none"
  )+
  labs(y="Percentage of all studies", x="Year")


ggsave("Figure2.png",dpi=300,height=4.5,width=7,bg="white")

```


<br> <br>

# Figure 3

```{r}
data %>% 
  filter(TS_SR_yn==T) %>% 
  select(StudyId,G_Year_Pub,SR_protocol,SR_databases,SR_searchstring,SR_reviewers,SR_flowchart,SR_rob,SR_metanaalysis) %>% 
  group_by(G_Year_Pub) %>% 
  mutate(SRs_per_Year=n()) %>%
  ungroup() %>% 
  pivot_longer(!c(StudyId,G_Year_Pub,SRs_per_Year)) %>% 
  filter(value==T) %>% 
  group_by(G_Year_Pub) %>% mutate(order_label=1:n(),label=ifelse(order_label==1,SRs_per_Year,NA)) %>% ungroup() %>% 
  group_by(name,G_Year_Pub,label) %>% 
  count() %>% 
  merge(.,data %>% filter(TS_SR_yn==T) %>% group_by(G_Year_Pub) %>% count() %>% rename(n_SR_per_Year=n),by="G_Year_Pub") %>% 
  mutate(perc_SR=n/n_SR_per_Year) %>% 
  filter(name!="SR_databases") %>%
  mutate(name=gsub("SR_","",name),
         name=str_to_title(name))  %>% 
  mutate(name=case_when(
    name=="Searchstring"~"Search string",
    name=="Metanaalysis"~"Meta-analysis",
    name=="Rob"~"Risk of bias",
    TRUE~name
  )) %>% 
  group_by(name) %>% mutate(order_facet=sum(n)) %>% ungroup() %>%
  mutate(facet_var_ordered = factor(name, levels = unique(name[order(-order_facet)]))) %>% 
  ggplot(aes(x=G_Year_Pub,y=perc_SR))+
  geom_bar(stat="identity",aes(fill=name)) +
  # geom_text(aes(label=label,y=0))+
  facet_wrap(.~facet_var_ordered)+
  scale_fill_manual(values=c("#fd7f6f", "#7eb0d5", "#b2e061", "#bd7ebe", "#ffb55a", "#ffee65", "#beb9db"))+
  theme_minimal()+
  theme(
    panel.grid.minor = element_blank(),
    legend.title = element_blank(),
    plot.margin = margin(0, 15, 0, 0),
    legend.position = "none"
  )+
  labs(y="Percentage of all studies", x="Year")

ggsave("Figure3.png",dpi=300,height=4.5,width=7,bg="white")


```

<br> <br>

# Systematic Reviews items

Important: even if a systematic review wasn't recorded because it didn't fit our inclusion criteria, we recorded each item independently (for instance: in a report a systematic review was conducted, a flowchart reported, involving two reviewers, but only 1 database was searched. This wouldn't categorize as SR, but the item flowchart and reviewers were recorded) <br>

```{r}
data_summary_SRs<-data %>% 
  select(G_Year_Pub,starts_with("SR_"),-SR_n_databases) %>% 
  pivot_longer(!G_Year_Pub) %>% 
  mutate(value=ifelse(value==T,1,0)) %>% 
  group_by(G_Year_Pub,name,value) %>% 
  summarise(n=sum(value)) %>% 
  ungroup() %>% 
  filter(value==1) %>% 
  group_by(name) %>% mutate(n_per_studytype=sum(n)) %>% ungroup() %>% 
  group_by(G_Year_Pub) %>% mutate(n_per_year=sum(n)) %>% ungroup()
  
data_summary_SRs %>% 
select(name,n_per_studytype) %>% 
  unique() %>% 
  arrange(-n_per_studytype) %>% 
  mutate(name=gsub("SR_","",name),
         name=str_to_sentence(name),
         name=gsub("Searchstring","Search string",name),
         name=gsub("Metanaalysis","Meta-analysis",name)
         ) %>% 
  rbind(.,cbind(name="Total reports",n_per_studytype=nrow(DataExtractionTable))) %>% 
  rename(`Study type`=name,
         n=n_per_studytype) %>% 
  kbl(caption = "Overview of the types of SR items extracted") %>% 
  kable_styling(full_width = F,position ="left")
```


<br> <br>

### Databases used

```{r}
databases_SR_n<-pull(data %>% 
  select(SR_n_databases) %>% 
  drop_na())
```

The number database used ranged from `r min(databases_SR_n)` to `r max(databases_SR_n)`, with a median of `r median(databases_SR_n)`

### Classification of reviews

```{r}
items_extracted_SR_count<-data %>% 
  select(TS_SR_yn,c(starts_with("SR_"),-SR_n_databases,-starts_with("SR_label_"))) %>%
  mutate(Any_SR_True = rowSums(select(., starts_with("SR_")) == TRUE) > 0) %>% 
  select(TS_SR_yn,Any_SR_True) %>% 
  summarise(SR_extracted=sum(TS_SR_yn),
            SR_items=sum(Any_SR_True))
```

`r sum(data$SR_label_ELS)` reviews were classified as ELS (extensive literature reviews). `r sum(data$SR_label_SR)` reviews were classified as systematic reviews.`r sum(data$TS_SR_yn)-(sum(data$SR_label_ELS)+sum(data$SR_label_SR))` were classified as neither, but were annotated by us as SR.

Even though only `r items_extracted_SR_count$SR_extracted` SRs were extracted according to our a-priori criteria, various items of a systematic review were extracted from `r items_extracted_SR_count$SR_items` studies.

<br><br>

```{r}
# save.image("image.RData")
```




### Additional figures - not in the MS
```{r include=F}
data_summary_SRs %>% 
  filter(name!="SR_label_SR") %>% 
  filter(name!="SR_label_ELS") %>% 
  filter(name!="SR_label_LR") %>% 
  select(G_Year_Pub,name,n) %>% 
  merge(.,data %>% group_by(G_Year_Pub) %>% count() %>% rename(n_studies_per_year=n),by="G_Year_Pub",all.y=T) %>% 
  group_by(G_Year_Pub) %>% mutate(count_col_label=1:n()) %>% ungroup() %>% 
  mutate(count_col_label=ifelse(count_col_label==1,n_studies_per_year,NA),
         name=gsub("SR_","",name), 
         name=str_to_sentence(name)) %>% 
  ggplot(aes(x=G_Year_Pub))+
  # geom_col(aes(y=count_col_label))+
  geom_bar(aes(y=n,fill=name),stat="identity",position="fill")+
  theme_minimal()+
  theme(
    panel.grid.minor = element_blank(),
    legend.title = element_blank()
  )+
  scale_fill_manual(values=c("#fd7f6f", "#7eb0d5", "#b2e061", "#bd7ebe", "#ffb55a", "#ffee65", "#beb9db"))+
  labs(x="Year",y="Proportion of items of SRs")

data_summary_SRs %>% 
  filter(name!="SR_label_SR") %>% 
  filter(name!="SR_label_ELS") %>% 
  filter(name!="SR_label_LR") %>% 
  select(G_Year_Pub,name,n) %>% 
  merge(.,data %>% group_by(G_Year_Pub) %>% count() %>% rename(n_studies_per_year=n),by="G_Year_Pub",all.y=T) %>% 
  group_by(G_Year_Pub) %>% mutate(count_col_label=1:n()) %>% ungroup() %>% 
  mutate(count_col_label=ifelse(count_col_label==1,n_studies_per_year,NA),
         name=gsub("SR_","",name), 
         name=str_to_sentence(name)) %>% 
  ggplot(aes(x=G_Year_Pub))+
  # geom_col(aes(y=count_col_label))+
  geom_bar(aes(y=n,fill=name),stat="identity")+
  theme_minimal()+
  theme(
    panel.grid.minor = element_blank(),
    legend.title = element_blank()
  )+
  scale_fill_manual(values=c("#fd7f6f", "#7eb0d5", "#b2e061", "#bd7ebe", "#ffb55a", "#ffee65", "#beb9db"))+
  labs(x="Year")

data %>% 
  select(StudyId,G_Year_Pub,starts_with("TS_"),-c(TS_SR_n,TS_other)) %>% 
  pivot_longer(cols = starts_with("TS_")) %>% 
  filter(value==T) %>% 
  group_by(G_Year_Pub,name) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(name=gsub("TS_","",name),
         name=case_when(name=="Literature_review"~"Literature review",
                   name=="SR_yn"~"Systematic review",
                   name=="Primary_study"~"Primary study",
                   TRUE~name
                   )) %>% 
  mutate(name=factor(name,levels=c("Primary study","Observational","Database","Survey","Systematic review","AHL","Literature review"))) %>% 
  merge(.,data %>% group_by(G_Year_Pub) %>% count() %>% rename(n_per_year=n),by="G_Year_Pub") %>% 
  group_by(G_Year_Pub) %>% 
  mutate(order=1:n(),label=ifelse(order==1,n_per_year,NA)) %>% 
  ggplot(aes(x=G_Year_Pub,y=n))+
  geom_bar(stat="identity",aes(fill=name))+
  theme_minimal()+
  theme(
    legend.title = element_blank(),
    panel.grid.minor = element_blank()
  )+
    scale_fill_manual(values=c("#b2e061", "#fd7f6f", "#ffee65", "#beb9db", "#ffb55a", "#7eb0d5","#dedede"))+
  labs(x="Year",y="n types of study")

data %>% 
  select(StudyId,G_Year_Pub,starts_with("TS_"),-c(TS_SR_n,TS_other)) %>% 
  pivot_longer(cols = starts_with("TS_")) %>% 
  filter(value==T) %>% 
  group_by(G_Year_Pub,name) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(name=gsub("TS_","",name),
         name=case_when(name=="Literature_review"~"Literature review",
                   name=="SR_yn"~"Systematic review",
                   name=="Primary_study"~"Primary study",
                   TRUE~name
                   )) %>% 
  mutate(name=factor(name,levels=c("Primary study","Observational","Database","Survey","Systematic review","AHL","Literature review"))) %>% 
  merge(.,data %>% group_by(G_Year_Pub) %>% count() %>% rename(n_per_year=n),by="G_Year_Pub") %>% 
  group_by(G_Year_Pub) %>% 
  mutate(order=1:n(),label=ifelse(order==1,n_per_year,NA)) %>% 
  ggplot(aes(x=G_Year_Pub,y=n))+
  geom_bar(stat="identity",position="fill",aes(fill=name))+
  geom_text(aes(label=label,y=0),position=position_nudge(y=0.03))+
  theme_minimal()+
  theme(
    legend.title = element_blank(),
    panel.grid.minor = element_blank()
  )+
    scale_fill_manual(values=c("#b2e061", "#fd7f6f", "#ffee65", "#beb9db", "#ffb55a", "#7eb0d5","#dedede"))+
  labs(x="Year",y="Proportion of types of study")
```













